NoTitle

### 2017-06-12 Aplas17/sections/Formalization.tex
changes

In this section, we present a formalization of our MIM calculus, based on
a minimal subset of Java 8 interfaces. The syntax, typing rules and small-step
semantics are included below.

\subsection{Syntax}
Figure~\ref{fig:syntax} shows the syntax of MIM. The multiple inheritance feature
of MIM has a basis on Java interfaces. To demonstrate how unintentional method conflicts
are untangled in MIM, we present the calculus in a straightforward way, hence we only
focus on a small subset of the interface model. For example, all the methods declared in an
interface are default methods, that is to say, they always provide default implementations.
From this point we can view that we are actually modelling a class model that supports multiple
inheritance. Then it is straightforward to do object creation like $\new I$. Fields and
primitive types are not modelled as well.

We use uppercase letters like $I, J, K$ to represent identifiers for interfaces. By multiple inheritance,
an interface can have a set of super interfaces, where such a set can be empty. Inside an interface are a
set of method declarations. Each method body holds a return statement. As seen in Figure~\ref{fig:syntax},
we have introduced the \kwoverride keyword to override an old implementation of the method. If the interface
that it overrides is exactly the enclosing interface, then such a method is seen as ``originally defined''.
Again for simplicity, overloading is not modelled for methods, which implies we can uniquely identify a method
by its name.

>>>>

In this section, we present a formalization of our MIM calculus, based on
a minimal subset of Java 8 interfaces.\bruno{Mention that it is done 
in a FJ style?} The syntax, typing rules and small-step
semantics are included below.

\subsection{Syntax}

Figure~\ref{fig:syntax} shows the syntax of MIM. The multiple
inheritance feature of MIM as a basis Java 8 interfaces, which support
method implementations via default methods. This feature is quite
closely related to \emph{traits}\cite{}.  To demonstrate how
unintentional method conflicts are untangled in MIM, we present the
calculus in a straightforward way, hence we only focus on a small
subset of the interface model. For example, all the methods declared
in an interface are default methods, that is to say, they always
provide default implementations.  From this point we can view that we
are actually modelling a class model that supports multiple
inheritance. Then it is straightforward to do object creation like
$\new I$. Fields and primitive types are not modelled as well.

We use uppercase letters like $I, J, K$ to represent identifiers for
interfaces. By multiple inheritance, an interface can have a set of
super interfaces, where such a set can be empty. Inside an interface
is a set of method declarations. Each method body holds a return
statement. As seen in Figure~\ref{fig:syntax}, we have introduced the
\kwoverride keyword\bruno{use \\xspace to deal with the spacing issues
in commands like override} to override an old implementation of the
method. If the interface that it overrides is exactly the enclosing
interface, then such a method is seen as ``originally defined''.
Again for simplicity, overloading is not modelled for methods, which
implies we can uniquely identify a method by its name.
